SIMD\slash SIMT-vectorized Thermo-chemical Source Term Evaluation

### 2018-01-31 derivations.tex
reorder and cleanup

\newcommand{\pluseq}{\mathrel{{+}{=}}}
\newcommand{\minuseq}{\mathrel{{-}{=}}}
\newcommand{\ns}{N_{sp}}
\newcommand{\nr}{N_{reac}}
\newcommand{\conp}{CONP}
\newcommand{\conv}{CONV}
\newcommand{\dconp}{\ifmmode\text{for \conp,}\else for \conp,\fi}
\newcommand{\dconv}{\ifmmode\text{for \conv,}\else for \conv.\fi}
\newcommand{\Ru}{\mathcal{R}}

@@

\subsubsection{Molar derivative}
Next the molar derivatives of the energy equation:
\begin{align}
 \mathcal{J}_{1,j} = \frac{\partial\dot{T}}{\partial{n_j}}
\end{align}

@@

Similar to~\cref{s:denergy_dt} the derivative of the energy equation with respect to the moles of species $j$---after collapsing the specific-heat\slash~concentration sum---are given by:
\begin{align}
 \frac{\partial\dot{T}}{\partial{n_j}} &= \frac{\left(\sum_{k=1}^{-1 + \ns} \left(H_{k} - \frac{W_{k} H_{\ns}}{W_{\ns}}\right) \dot{\omega}_{k}\right) \sum_{k=1}^{-1 + \ns} - \frac{\delta_{j k}}{V} \left({C_p}_{\ns} - {C_p}_{k}\right)}{\left(\sum_{k=1}^{\ns} [C]_{k} {C_p}_{k}\right)^{2}} - \nonumber \\ 
				       & \mathindent \frac{1}{\sum_{k=1}^{\ns} [C]_{k} {C_p}_{k}} \sum_{k=1}^{-1 + \ns} \left(H_{k} - \frac{W_{k} H_{\ns}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial {n_j} }_{k}
\end{align}
Next, the Kronecker delta summation is simplified, and the the compact form of the energy equation factored out yielding:
\begin{subequations}
\begin{align}
 \frac{\partial\dot{T}}{\partial{n_j}} &= \frac{1}{\sum_{k=1}^{\ns} [C]_{k} {C_p}_{k}} \Biggl[- \sum_{k=1}^{-1 + \ns} \left(H_{k} - \frac{W_{k} H_{\ns}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial {n_j} }_{k} & \nonumber \\
				       &  \mathindent[largerindentand] - \frac{1}{V} \frac{\text{d} T }{\text{d} t } \left(- {C_p}_{\ns} + {C_p}_{j}\right)\Biggr] & \text{\dconp} \\
\intertext{and:}
 \frac{\partial\dot{T}}{\partial{n_j}} &= \frac{1}{\sum_{k=1}^{\ns} [C]_{k} {C_v}_{k}} \Biggl[- \sum_{k=1}^{-1 + \ns} \left(U_{k} - \frac{W_{k} U_{\ns}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial {n_j} }_{k} & \nonumber \\ 
				       & \mathindent[largerindentand] - \frac{1}{V} \frac{\text{d} T }{\text{d} t } \left(- {C_v}_{\ns} + {C_v}_{j}\right) \Biggr] & \text{\dconv}
\end{align}
\end{subequations}
Again, the species production rate derivative with respect to moles will be explored in~\cref{s:d_spec_prod}.

\subsubsection{State parameter derivatives}
Next, the derivative of the energy equation with respect to the thermodynamic state parameter will be considered:
\begin{subequations}
\begin{align}
 \mathcal{J}_{1, 2} & = \frac{\partial\dot{T}}{\partial{V}} & \text{\dconp} \\
 \mathcal{J}_{1, 2} & = \frac{\partial\dot{T}}{\partial{P}} & \text{\dconv}
\end{align}
\end{subequations}

First, the derivative of the concentration of a species $k$ with respect to the state parameter is:
\begin{subequations}
 \label{e:dck_de}
 \begin{align}
 \lhs{dck}{\frac{\partial [C]_{k} }{\partial V }} &=
  \begin{dcases}
  \rhs{dck}{-\frac{[C]_{k}}{V}} & \mathcond{dck}{k \ne \ns} \\
  \rhs{dck}{\frac{1}{V} \sum_{k=1}^{\ns  - 1} [C]_{k}} & \mathcond{dck}{k = \ns}
 \end{dcases}&\cond{dck}{\dconp} \\
 \lhs{dck}{\frac{\partial [C]_{k} }{\partial P }} &=
 \begin{dcases}
   \rhs{dck}{\mathindent[s]0} & \mathcond{dck}{k \ne \ns} \\
   \rhs{dck}{\frac{1}{T \Ru}} & \mathcond{dck}{k = \ns}
 \end{dcases}&\cond{dck}{\dconv}
 \end{align}
\end{subequations}
while the specific heat and enthalpy\slash internal-energy are independent of the state parameter for both \conp~and \conv.
Following the now familiar collapsing of the specific-heat\slash concentration sum, and substituting in the energy source term gives:
\loadeq{dTdParam}
Finally, the species production rate derivative with respect to the state parameter will be computed in~\cref{s:d_spec_prod}.

@@

@@

Similarly, the derivative of the net molar rate of production of a species $k$ with respect to the moles of species $j$ is:
\begin{align}
 \mathcal{J}_{k + 2, j + 2} &= \frac{\partial }{\partial n_j } \frac{\text{d} n_{k}}{\text{d} t} = \frac{\partial \dot{n}_k }{\partial n_j } \nonumber \\
  \intertext{or:}
 \mathcal{J}_{k + 2, j + 2} & = V \frac{\partial \dot{\omega}_{k} }{\partial {n_j} }
\end{align}

Finally, the derivative of the net molar rate of production of a species $k$ with respect to the state parameter is:
\begin{subequations}
\begin{align}
  \mathcal{J}_{k + 2, 2} &= \frac{\partial }{\partial V } \frac{\text{d} n_{k}}{\text{d} t} = \frac{\partial \dot{n}_k }{\partial V } & \nonumber \\
			 &= V \frac{\partial \dot{\omega}_{k} }{\partial V } + \dot{\omega}_{k} & \text{\dconp}
  \intertext{and:}
  \mathcal{J}_{k + 2, 2} &= \frac{\partial }{\partial P } \frac{\text{d} n_{k}}{\text{d} t} = \frac{\partial \dot{n}_k }{\partial P } & \nonumber \\
			 &=V \frac{\partial \dot{\omega}_{k} }{\partial P } & \text{\dconv}
\end{align}
\end{subequations}

\subsubsection{Molar derivative}
Similarly, the derivatives of the thermodynamic state parameter source terms with respect to the moles of species $j$ are:
\begin{align}
 \mathcal{J}_{2, j + 2} &= \frac{\partial }{\partial n_j } \frac{\text{d} V}{\text{d} t} = \frac{\partial \dot{V} }{\partial n_j} & \nonumber \\
		    &= V \left(\frac{1}{[C]} \sum_{k=1}^{-1 + \ns} \left(1 - \frac{W_{k}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial {n_j} }_{k} + \frac{1}{T} \frac{\text{d} \dot{T} }{\text{d} {n_j} }\right) & \text{\dconp}
\intertext{and:}
 \mathcal{J}_{2, j + 2} &= \frac{\partial }{\partial n_j } \frac{\text{d} V}{\text{d} t} = \frac{\partial \dot{P} }{\partial n_j} & \nonumber \\
		    &=  \frac{P}{T} \frac{\text{d} \dot{T} }{\text{d} {n_j} } + T \Ru \sum_{k=1}^{-1 + \ns} \left(1 - \frac{W_{k}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial {n_j} }_{k} & \text{\dconv}
\end{align}

\subsubsection{State parameter derivative}
Finally, the derivative of the the thermodynamic state parameter source terms with respect to themselves are:
\begin{align}
 \mathcal{J}_{2, 2} &= \frac{\partial }{\partial V } \frac{\text{d} V}{\text{d} t} = \frac{\partial \dot{V} }{\partial V} & \nonumber \\
		    &= \frac{1}{[C]} \sum_{k=1}^{-1 + \ns} \left(1 - \frac{W_{k}}{W_{\ns}}\right) \left(V \frac{\partial \dot{\omega} }{\partial V }_{k} + \dot{\omega}_{k}\right) \nonumber \\
		    & \mathindent + \frac{1}{T} \left(V \frac{\text{d} \dot{T} }{\text{d} V } + \dot{T}\right) & \text{\dconp} \\
 \intertext{and:}
 \mathcal{J}_{2, 2} &= \frac{\partial }{\partial P } \frac{\text{d} P}{\text{d} t} = \frac{\partial \dot{P} }{\partial P} & \nonumber \\
		    &= T \Ru \sum_{k=1}^{-1 + \ns} \left(1 - \frac{W_{k}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial P }_{k} & \nonumber \\ 
		    & \mathindent + \frac{1}{T} \left(P \frac{\text{d} \dot{T} }{\text{d} P } + \dot{T}\right) & \text{\dconv}
\end{align}

\subsection{Species production rate derivatives}
\label{s:d_spec_prod}
First, we evaluate the derivatives of the net species production rate equation~\cref{e:spec_rop}, with respect to temperature:
\begin{align}
 \label{e:dwdot_dT}
 \lhs{dwdot}{\frac{\partial \dot{\omega} }{\partial T }_{k}} &= \rhs{dwdot}{\sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial T }_{i} + \nu_{k,i} \frac{\partial R }{\partial T }_{i} c_{i}\right)} & \cond{dwdot}{,}
\end{align}
other species:
\begin{align}
 \label{e:dwdot_dnj}
 \lhs{dwdot}{\frac{\partial \dot{\omega} }{\partial {n_j} }_{k}} &= \rhs{dwdot}{\sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial {n_j} }_{i} + \nu_{k,i} \frac{\partial R }{\partial {n_j} }_{i} c_{i}\right)} & \cond{dwdot}{,}
\end{align}
and the state parameter:
\begin{subequations}
 \label{e:dwdot_de}
 \begin{align}
  \lhs{dwdot}{\frac{\partial \dot{\omega} }{\partial V }_{k}} &= \rhs{dwdot}{\sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial V }_{i} + \nu_{k,i} \frac{\partial R }{\partial V }_{i} c_{i}\right)} & \cond{dwdot}{\dconp}\\
  \lhs{dwdot}{\frac{\partial \dot{\omega} }{\partial P }_{k}} &= \rhs{dwdot}{\sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial P }_{i} + \nu_{k,i} \frac{\partial R }{\partial P }_{i} c_{i}\right)} & \cond{dwdot}{\dconv}
 \end{align}
\end{subequations}

\subsection{Rate of progress derivatives}
\subsubsection{Temperature derivative}
\label{s:dri_dt}
Next, the rate of progress derivatives are evaluated, first with respect to temperature:
\begin{equation}
 \frac{\partial R }{\partial T }_{i} = \frac{\partial}{\partial T}\left({k_{f, i}} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}}\right)
\end{equation}
The derivative of the forward reaction rate coefficient is:
\begin{equation}
 \label{e:dkf_dt}
 \frac{\text{d} {k_f} }{\text{d} T }_{i} = \frac{{k_{f, i}}}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)
\end{equation}
While evaluating derivatives for the Jacobian, it is important to expand terms---e.g., concentration, production rate, etc.---related to the last species to obtain the correct derivative, in this case using \cref{e:last_spec_conc}:
\begin{equation}
 {R_f} = \left(\left(- \sum_{k=1}^{\ns  - 1} [C]_{k} + \frac{P}{T \Ru}\right)^{\nu^{\prime}_{\ns,i}}\right) {k_{f, i}} \prod_{k=1}^{\ns  - 1} [C]_{k}^{\nu^{\prime}_{k,i}}
\end{equation}

@@

Finally, combining~\cref{e:dropf_dt,e:dropr_dt} gives the total temperature derivative of the net rate of progress:
\loadeq{dropdT}
\subsubsection{Molar derivative}
\label{s:dri_dnj}
The derivative of the forward rate of progress with respect to the amount of moles of a species $j$ is:
\begin{equation}
 \label{e:dropf_dnj_1}
 \frac{d}{d n_{k}} {R_{f_i}} = \left(\frac{\partial}{\partial n_{j}} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}}\right) {k_{f, i}} \;.
\end{equation}

@@

\subsubsection{Pressure-dependent reactions}
\label{s:dri_pdep}
The P-Log and Chebyshev pressure-dependent reactions, described by~\cref{e:kf_plog,e:kf_cheb} require separate treatment from the derivatives of strictly Arrhenius-based reaction rate formulations examined in~\cref{s:dri_dt,s:dri_dnj,s:dri_de}.
Beginning with P-Log reactions, the derivative of the forward rate coefficient with respect to temperature is:
\begin{align}
 \frac{\partial {k_{f, i}} }{\partial T } &= \biggl( \frac{1}{k_{1}} \frac{\text{d} k_1 }{\text{d} T } + \frac{1}{- \log{\left (P_{1} \right )} + \log{\left (P_{2} \right )}} \left(- \frac{1}{k_{1}} \frac{\text{d} k_1 }{\text{d} T } + \frac{1}{k_{2}} \frac{\text{d} k_2 }{\text{d} T }\right) \times  \Bigl( \nonumber \\
					 & \mathindent - \log{\left (P_{1} \right )} + \log{\left (P \right )}\Bigr)\biggr) {k_{f, i}}
\end{align}
while the derivatives of $k_{1}$ and $k_{2}$ are given by~\cref{e:dkf_dt}---with the corresponding Arrhenius parameters (see~\cref{e:plog_k1,e:plog_k2}) substituted in.
Simplifying gives:
\begin{align}
 \label{e:dkf_plog_dt}
 \frac{\partial {k_{f, i}} }{\partial T } &= \frac{{k_{f, i}}}{T} \Biggl(\frac{\left(- \log{\left (P_{1} \right )} + \log{\left (P \right )}\right) \left(- \beta_1 + \beta_2 - \frac{E_{a_1}}{T \Ru} + \frac{E_{a_2}}{T \Ru}\right)}{- \log{\left (P_{1} \right )} + \log{\left (P_{2} \right )}} + \nonumber \\
					 & \mathindent[morespac] \beta_1 + \frac{E_{a_1}}{T \Ru}\Biggr)
\end{align}
Similar to~\cref{s:dri_dt},~\cref{e:dkf_plog_dt} may be substituted into~\cref{e:dropfdt_1,e:droprdt_1} to give:
\loadeq{dropplogdT}

@@

\subsection{Pressure modification\slash Falloff function derivatives}
\label{s:dpmod_fall}
\subsubsection{Elementary reactions}
For elementary reactions, all derivatives of the pressure-modification term are zero:
\begin{align}
\lhs{dci_elem}{\frac{\partial c_{i} }{\partial T }} &= \rhs{dci_elem}{0} & \cond{dci_elem}{,} \label{e:dci_elem_dt} \\
\lhs{dci_elem}{\frac{\partial c_{i} }{\partial {n_j} }} &= \rhs{dci_elem}{0} & \cond{dci_elem}{,} \label{e:dci_elem_dnj} \\
\end{align}
and:
\begin{subequations}
 \label{e:dci_elem_de}
 \begin{align}
  \lhs{dci_elem}{\frac{\partial c_{i} }{\partial V }} &= \rhs{dci_elem}{0} & \cond{dci_elem}{\dconp} \\
  \lhs{dci_elem}{\frac{\partial c_{i} }{\partial P }} &= \rhs{dci_elem}{0} & \cond{dci_elem}{\dconv}
 \end{align}
\end{subequations}

>>>>

\newcommand{\pluseq}{\mathrel{{+}{=}}}
\newcommand{\minuseq}{\mathrel{{-}{=}}}
\newcommand{\ns}{N_{sp}}
\newcommand{\nr}{N_{reac}}
\newcommand{\conp}{CONP}
\newcommand{\conv}{CONV}
\newcommand{\dconp}{\ifmmode\text{for \conp,}\else for \conp,\fi}
\newcommand{\dconv}{\ifmmode\text{for \conv,}\else for \conv,\fi}
\newcommand{\Ru}{\mathcal{R}}

@@

\subsubsection{State parameter derivatives}
Next, the derivative of the energy equation with respect to the thermodynamic state parameter will be considered:
\begin{subequations}
\label{e:dTdotdE_initial}
\begin{align}
 \mathcal{J}_{1, 2} & = \frac{\partial\dot{T}}{\partial{V}} & \text{\dconp} \\
 \mathcal{J}_{1, 2} & = \frac{\partial\dot{T}}{\partial{P}} & \text{\dconv}
\end{align}
\end{subequations}

First, the derivative of the concentration of a species $k$ with respect to the state parameter is:
\begin{subequations}
 \label{e:dck_de}
 \begin{align}
 \lhs{dck}{\frac{\partial [C]_{k} }{\partial V }} &=
  \begin{dcases}
  \rhs{dck}{-\frac{[C]_{k}}{V}} & \mathcond{dck}{k \ne \ns} \\
  \rhs{dck}{\frac{1}{V} \sum_{k=1}^{\ns  - 1} [C]_{k}} & \mathcond{dck}{k = \ns}
 \end{dcases}&\cond{dck}{\dconp} \\
 \lhs{dck}{\frac{\partial [C]_{k} }{\partial P }} &=
 \begin{dcases}
   \rhs{dck}{\mathindent[s]0} & \mathcond{dck}{k \ne \ns} \\
   \rhs{dck}{\frac{1}{T \Ru}} & \mathcond{dck}{k = \ns}
 \end{dcases}&\cond{dck}{\dconv}
 \end{align}
\end{subequations}
while the specific heat and enthalpy\slash internal-energy are independent of the state parameter for both \conp~and \conv.
Following the same procedure as in~\cref{s:denergy_dt}, the result of~\cref{e:dTdotdE_initial} are simplified by collapsing the specific-heat\slash concentration sum, and substituting in the temperature source term, giving:
\begin{subequations}
\begin{align}
 \frac{\partial\dot{T}}{\partial{V}} &= \frac{1}{\sum_{k=1}^{\ns} [C]_{k} {C_p}_{k}} \Biggl[ - \sum_{k=1}^{-1 + \ns} \left(H_{k} - \frac{W_{k} H_{\ns}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial V }_{k} + & \nonumber \\
				     & \mathindent[largerindentand] \frac{1}{V} \frac{\text{d} T }{\text{d} t } \sum_{k=1}^{-1 + \ns} \left(- {C_p}_{\ns} + {C_p}_{k}\right) [C]_{k}\Biggr] & \text{\dconp} \\
 \frac{\partial\dot{T}}{\partial{P}} &= \frac{1}{\sum_{k=1}^{\ns} [C]_{k} {C_v}_{k}} \Biggl[- \sum_{k=1}^{-1 + \ns} \left(U_{k} - \frac{W_{k} U_{\ns}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial P }_{k} - & \nonumber \\
				     & \mathindent[largerindentand] \frac{{C_v}_{\ns}}{T \Ru} \frac{\text{d} T }{\text{d} t } \Biggr] & \text{\dconv}
\end{align}
\end{subequations}
The derivative of the species production rate with respect to the state parameter will be computed in~\cref{s:d_spec_prod}.

\subsubsection{Molar derivative}
Finally, the molar derivative of the temperature source term is:
\begin{align}
 \mathcal{J}_{1,j} = \frac{\partial\dot{T}}{\partial{n_j}}
\end{align}

@@

Similar to~\cref{s:denergy_dt} the derivative of the energy equation with respect to the moles of species $j$---after collapsing the specific-heat\slash~concentration sum---are given by:
\begin{align}
 \frac{\partial\dot{T}}{\partial{n_j}} &= \frac{\left(\sum_{k=1}^{-1 + \ns} \left(H_{k} - \frac{W_{k} H_{\ns}}{W_{\ns}}\right) \dot{\omega}_{k}\right) \sum_{k=1}^{-1 + \ns} - \frac{\delta_{j k}}{V} \left({C_p}_{\ns} - {C_p}_{k}\right)}{\left(\sum_{k=1}^{\ns} [C]_{k} {C_p}_{k}\right)^{2}} - \nonumber \\
				       & \mathindent \frac{1}{\sum_{k=1}^{\ns} [C]_{k} {C_p}_{k}} \sum_{k=1}^{-1 + \ns} \left(H_{k} - \frac{W_{k} H_{\ns}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial {n_j} }_{k}
\end{align}
Next, the Kronecker delta summation is simplified, and the the compact form of the energy equation factored out yielding:
\begin{subequations}
\begin{align}
 \frac{\partial\dot{T}}{\partial{n_j}} &= \frac{1}{\sum_{k=1}^{\ns} [C]_{k} {C_p}_{k}} \Biggl[- \sum_{k=1}^{-1 + \ns} \left(H_{k} - \frac{W_{k} H_{\ns}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial {n_j} }_{k} & \nonumber \\
				       &  \mathindent[largerindentand] - \frac{1}{V} \frac{\text{d} T }{\text{d} t } \left(- {C_p}_{\ns} + {C_p}_{j}\right)\Biggr] & \text{\dconp} \\
\intertext{and:}
 \frac{\partial\dot{T}}{\partial{n_j}} &= \frac{1}{\sum_{k=1}^{\ns} [C]_{k} {C_v}_{k}} \Biggl[- \sum_{k=1}^{-1 + \ns} \left(U_{k} - \frac{W_{k} U_{\ns}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial {n_j} }_{k} & \nonumber \\
				       & \mathindent[largerindentand] - \frac{1}{V} \frac{\text{d} T }{\text{d} t } \left(- {C_v}_{\ns} + {C_v}_{j}\right) \Biggr] & \text{\dconv}
\end{align}
\end{subequations}
Again, the derivative of the species production rate with respect to moles will be explored in~\cref{s:d_spec_prod}.

\subsubsection{State parameter derivative}
Similarly, the derivative of the the thermodynamic state parameter source terms with respect to themselves are:
\begin{align}
 \mathcal{J}_{2, 2} &= \frac{\partial }{\partial V } \frac{\text{d} V}{\text{d} t} = \frac{\partial \dot{V} }{\partial V} & \nonumber \\
		    &= \frac{1}{[C]} \sum_{k=1}^{-1 + \ns} \left(1 - \frac{W_{k}}{W_{\ns}}\right) \left(V \frac{\partial \dot{\omega} }{\partial V }_{k} + \dot{\omega}_{k}\right) \nonumber \\
		    & \mathindent + \frac{1}{T} \left(V \frac{\text{d} \dot{T} }{\text{d} V } + \dot{T}\right) & \text{\dconp} \\
 \intertext{and:}
 \mathcal{J}_{2, 2} &= \frac{\partial }{\partial P } \frac{\text{d} P}{\text{d} t} = \frac{\partial \dot{P} }{\partial P} & \nonumber \\
		    &= T \Ru \sum_{k=1}^{-1 + \ns} \left(1 - \frac{W_{k}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial P }_{k} & \nonumber \\
		    & \mathindent + \frac{1}{T} \left(P \frac{\text{d} \dot{T} }{\text{d} P } + \dot{T}\right) & \text{\dconv}
\end{align}

\subsubsection{Molar derivative}
Finally, the derivatives of the thermodynamic state parameter source terms with respect to the moles of species $j$ are:
\begin{align}
 \mathcal{J}_{2, j + 2} &= \frac{\partial }{\partial n_j } \frac{\text{d} V}{\text{d} t} = \frac{\partial \dot{V} }{\partial n_j} & \nonumber \\
		    &= V \left(\frac{1}{[C]} \sum_{k=1}^{-1 + \ns} \left(1 - \frac{W_{k}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial {n_j} }_{k} + \frac{1}{T} \frac{\text{d} \dot{T} }{\text{d} {n_j} }\right) & \text{\dconp}
\intertext{and:}
 \mathcal{J}_{2, j + 2} &= \frac{\partial }{\partial n_j } \frac{\text{d} V}{\text{d} t} = \frac{\partial \dot{P} }{\partial n_j} & \nonumber \\
		    &=  \frac{P}{T} \frac{\text{d} \dot{T} }{\text{d} {n_j} } + T \Ru \sum_{k=1}^{-1 + \ns} \left(1 - \frac{W_{k}}{W_{\ns}}\right) \frac{\partial \dot{\omega} }{\partial {n_j} }_{k} & \text{\dconv}
\end{align}

@@

Similarly, the derivative of the net molar rate of production of a species $k$ with respect to the state parameter is:
\begin{subequations}
\begin{align}
  \mathcal{J}_{k + 2, 2} &= \frac{\partial }{\partial V } \frac{\text{d} n_{k}}{\text{d} t} = \frac{\partial \dot{n}_k }{\partial V } & \nonumber \\
			 &= V \frac{\partial \dot{\omega}_{k} }{\partial V } + \dot{\omega}_{k} & \text{\dconp}
  \intertext{and:}
  \mathcal{J}_{k + 2, 2} &= \frac{\partial }{\partial P } \frac{\text{d} n_{k}}{\text{d} t} = \frac{\partial \dot{n}_k }{\partial P } & \nonumber \\
			 &=V \frac{\partial \dot{\omega}_{k} }{\partial P } & \text{\dconv}
\end{align}
\end{subequations}

@@

Finally, the derivative of the net molar rate of production of a species $k$ with respect to the moles of species $j$ is:
\begin{align}
 \mathcal{J}_{k + 2, j + 2} &= \frac{\partial }{\partial n_j } \frac{\text{d} n_{k}}{\text{d} t} = \frac{\partial \dot{n}_k }{\partial n_j } \nonumber \\
  \intertext{or:}
 \mathcal{J}_{k + 2, j + 2} & = V \frac{\partial \dot{\omega}_{k} }{\partial {n_j} }
\end{align}

\subsection{Species production rate derivatives}
\label{s:d_spec_prod}
First, we evaluate the derivatives of the net species production rate equation~\cref{e:spec_rop}, with respect to temperature:
\begin{align}
 \label{e:dwdot_dT}
 \lhs{dwdot}{\frac{\partial \dot{\omega} }{\partial T }_{k}} &= \rhs{dwdot}{\sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c_{i}}{\partial T } + \nu_{k,i} \frac{\partial R_{i}}{\partial T } c_{i}\right)} & \cond{dwdot}{,}
\end{align}
the state parameter:
\begin{subequations}
 \label{e:dwdot_de}
 \begin{align}
  \lhs{dwdot}{\frac{\partial \dot{\omega} }{\partial V }_{k}} &= \rhs{dwdot}{\sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c_{i}}{\partial V } + \nu_{k,i} \frac{\partial R_{i}}{\partial V } c_{i}\right)} & \cond{dwdot}{\dconp}\\
  \lhs{dwdot}{\frac{\partial \dot{\omega} }{\partial P }_{k}} &= \rhs{dwdot}{\sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c_{i}}{\partial P } + \nu_{k,i} \frac{\partial R_{i}}{\partial P } c_{i}\right)} & \cond{dwdot}{\dconv}
 \end{align}
\end{subequations}
and other species:
\begin{align}
 \label{e:dwdot_dnj}
 \lhs{dwdot}{\frac{\partial \dot{\omega} }{\partial {n_j} }_{k}} &= \rhs{dwdot}{\sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial {n_j} }_{i} + \nu_{k,i} \frac{\partial R }{\partial {n_j} }_{i} c_{i}\right)} & \cond{dwdot}{,}
\end{align}

\subsection{Rate of progress derivatives}
\subsubsection{Temperature derivative}
\label{s:dri_dt}
Next, the rate of progress derivatives are evaluated, first with respect to temperature:
\begin{equation}
 \frac{\partial R_{i}}{\partial T } = \frac{\partial}{\partial T}\left({k_{f, i}} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}}\right)
\end{equation}
The derivative of the forward reaction rate coefficient is:
\begin{equation}
 \label{e:dkf_dt}
 \frac{\text{d} {k_f} }{\text{d} T }_{i} = \frac{{k_{f, i}}}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)
\end{equation}
While evaluating derivatives for the Jacobian, it is important to expand terms---e.g., concentration, production rate, etc.---related to the last species to obtain the correct derivative, in this case using \cref{e:last_spec_conc}:
\begin{equation}
 {R_f} = \left(\left(- \sum_{k=1}^{\ns  - 1} [C]_{k} + \frac{P}{T \Ru}\right)^{\nu^{\prime}_{\ns,i}}\right) {k_{f, i}} \prod_{k=1}^{\ns  - 1} [C]_{k}^{\nu^{\prime}_{k,i}}
\end{equation}

@@

Finally, combining~\cref{e:dropf_dt,e:dropr_dt} gives the total temperature derivative of the net rate of progress:
\begin{align}
 \label{e:drop_dT}
 \frac{\partial R_{i}}{\partial T } =& \frac{{R_{f, i}}}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right) - \left(- \sum_{k=1}^{\ns} \nu_{k,i} \frac{\text{d} B }{\text{d} T }_{k} + \frac{1}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)\right) {R_{r, i}} \nonumber \\
				      &\qquad + \frac{[C] S^{\prime\prime}_{\ns}}{T} {k_{r, i}} - \frac{[C] S^{\prime}_{\ns}}{T} {k_{f, i}}
\end{align}

\subsubsection{Molar derivative}
\label{s:dri_dnj}
The derivative of the forward rate of progress with respect to the amount of moles of a species $j$ is:
\begin{equation}
 \label{e:dropf_dnj_1}
 \frac{d}{d n_{k}} {R_{f_i}} = \left(\frac{\partial}{\partial n_{j}} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}}\right) {k_{f, i}} \;.
\end{equation}

@@

\subsubsection{Pressure-dependent reactions}
\label{s:dri_pdep}
The P-Log and Chebyshev pressure-dependent reactions, described by~\cref{e:kf_plog,e:kf_cheb} require separate treatment from the derivatives of strictly Arrhenius-based reaction rate formulations examined in~\cref{s:dri_dt,s:dri_dnj,s:dri_de}.
Beginning with P-Log reactions, the derivative of the forward rate coefficient with respect to temperature is:
\begin{align}
 \frac{\partial {k_{f, i}} }{\partial T } &= \biggl( \frac{1}{k_{1}} \frac{\text{d} k_1 }{\text{d} T } + \frac{1}{- \log{\left (P_{1} \right )} + \log{\left (P_{2} \right )}} \left(- \frac{1}{k_{1}} \frac{\text{d} k_1 }{\text{d} T } + \frac{1}{k_{2}} \frac{\text{d} k_2 }{\text{d} T }\right) \times  \Bigl( \nonumber \\
					 & \mathindent - \log{\left (P_{1} \right )} + \log{\left (P \right )}\Bigr)\biggr) {k_{f, i}}
\end{align}
while the derivatives of $k_{1}$ and $k_{2}$ are given by~\cref{e:dkf_dt}---with the corresponding Arrhenius parameters (see~\cref{e:plog_k1,e:plog_k2}) substituted in.
Simplifying gives:
\begin{align}
 \label{e:dkf_plog_dt}
 \frac{\partial {k_{f, i}} }{\partial T } &= \frac{{k_{f, i}}}{T} \Biggl(\frac{\left(- \log{\left (P_{1} \right )} + \log{\left (P \right )}\right) \left(- \beta_1 + \beta_2 - \frac{E_{a_1}}{T \Ru} + \frac{E_{a_2}}{T \Ru}\right)}{- \log{\left (P_{1} \right )} + \log{\left (P_{2} \right )}} + \nonumber \\
					 & \mathindent[morespac] \beta_1 + \frac{E_{a_1}}{T \Ru}\Biggr)
\end{align}
Similar to~\cref{s:dri_dt},~\cref{e:dkf_plog_dt} may be substituted into~\cref{e:dropfdt_1,e:droprdt_1} to give:
\begin{align}
 \label{e:drop_plog_dT}
 \frac{\partial R_{i} }{\partial T } &= \left(\frac{\left(- \log{\left (P_{1} \right )} + \log{\left (P \right )}\right) \left(- \beta_1 + \beta_2 - \frac{E_{a_1}}{T \Ru} + \frac{E_{a_2}}{T \Ru}\right)}{- \log{\left (P_{1} \right )} + \log{\left (P_{2} \right )}} + \beta_1 + \frac{E_{a_1}}{T \Ru} \right) \times \nonumber \\
				     & \mathindent \left(\frac{{R_{f, i}} - {R_{r, i}}}{T}\right) + {R_{r, i}} \sum_{k=1}^{\ns} \nu_{k,i} \frac{\text{d} B }{\text{d} T }_{k} + \frac{[C]}{T} \left(S^{\prime\prime}_{\ns} {k_{r, i}} - S^{\prime}_{\ns} {k_{f, i}}\right)
\end{align}

@@

\subsection{Pressure modification\slash Falloff function derivatives}
\label{s:dpmod_fall}
\subsubsection{Elementary reactions}
For elementary reactions, the derivative of the pressure-modification term with respect to temperature is:
\begin{align}
\lhs{dci_elem}{\frac{\partial c_{i} }{\partial T }} &= \rhs{dci_elem}{0} & \cond{dci_elem}{,} \label{e:dci_elem_dt}
\end{align}
the state parameter:
\begin{subequations}
 \label{e:dci_elem_de}
 \begin{align}
  \lhs{dci_elem}{\frac{\partial c_{i} }{\partial V }} &= \rhs{dci_elem}{0} & \cond{dci_elem}{\dconp} \\
  \lhs{dci_elem}{\frac{\partial c_{i} }{\partial P }} &= \rhs{dci_elem}{0} & \cond{dci_elem}{\dconv}
 \end{align}
\end{subequations}
and the moles:
\begin{align}
 \lhs{dci_elem}{\frac{\partial c_{i} }{\partial {n_j} }} &= \rhs{dci_elem}{0} & \cond{dci_elem}{.} \label{e:dci_elem_dnj}
\end{align}
